---
title: "Computation of kappa"
author: "Derumigny, A. , Guyonvarch Y. & Girard, L."
date: \today
output:
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Remember that $$\kappa_n := 
\sup_{t: \, |t| \geq a_n/\sqrt{n}} |f_{X_n/\sigma_n}(t)|.$$
with $a_n := 2 t_1^* \pi \sqrt{n} / (2 K_{3,n})$ for large $n$.

Furthermore, $t_1^* \pi \approx = 2.0106$
```{r}
0.64 * pi
```

Therefore,
$$\kappa_n \leq
\sup_{t: \, |t| \geq 2 / K_{3,n}} |f_{X_n/\sigma_n}(t)|.$$

# Normal distribution

For the normal distribution $K_{3,n} = \sqrt{2/pi}$ and $|f_{X_n/\sigma_n}(t)| = \exp(-t^2/2)$.
Therefore $\kappa_n$ is smaller than
```{r}
t = 2 / sqrt(2 / pi)
exp( - t^2 / 2)
```

# Laplace distribution

For the Laplace distribution $K_{3,n} = 6/2^{3/2}$ and $|f_{X_n/\sigma_n}(t)| = 1 / (1 + t^2/2)$.
Therefore $\kappa_n$ is smaller than
```{r}
t = 2 / (6 / 2^{3/2})
1 / (1 + t^2/2)
```


# Student distribution


```{r}
# Setting parameters
Nrep = 100000

t1 <- 0.64 # universal constant from paper
n<- 5000
nu <- 8 # df for student
K4_exp <- 9
K4_gauss <- 3
```

```{r}
# Absolute third order moment of exp distr upper bounded while that of
# standard normal distr explicitly computed

K3_exp <- K4_exp^(3/4)
K3_gauss <- 2^(3/2)*gamma(2)/sqrt(pi)
```


```{r}

# Function to compute a_n (cf article)

compute_an <- function(t1,n,K3) {
  
  build_an_1 <- 2*t1*pi*sqrt(n)/(K3+1)
  build_an_2 <- 16*pi^3*n^2/(K3+1)^4
  
  return( min(build_an_1,build_an_2)/sqrt(n) )
}


# Compute kappa_n for exp and standard normal

carac_exp_at_an <- 1 / sqrt(1 + compute_an(t1=t1,n=n,K3=K3_exp)^2)

carac_gauss_at_an <- exp( - compute_an(t1=t1,n=n,K3=K3_gauss)^2/2)


# Function to evaluate the characteristic function of 
# the Student distribution at some point of interest (here a_n)

stud_carac_fun <- function(t1, n, nu) {
  
  sigma <- sqrt(nu/(nu-2))
  K4 <- 6/(nu-4)+3
  an <- compute_an(t1=t1, n=n, K3= mean(abs(scale(rt(Nrep, df = nu)))^3) )
  temp1 <- besselK(nu = nu/2, x = sqrt(nu)*abs(an)/sigma)
  temp2 <- (sqrt(nu)*abs(an)/sigma)^(nu/2) / (gamma(nu/2)*2^(nu/2-1))
  
  return(temp1 * temp2)
}
```


```{r}
# compute kappa_n for the Student distribution

stud_carac_fun(t1=t1,n=n,nu=8)
stud_carac_fun(t1=t1,n=n,nu=5)
```

# Exponential distribution

The characteristic function of the exponential distribution is $1 / (1-it)$.
So the one we need is $1 / (1-it) * \exp(it)$ (which has the same modulus).

```{r}
an_Gamma = compute_an(t1=t1, n = 5000, K3 = 2.31)

sqrt((1 / (1 + an_Gamma^2)^2 )^2 + 
       (an_Gamma^2 / (1 + an_Gamma^2)^2 )^2 )

```


